Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-15 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Added figure description Nikolaev2010
Information on the rights for reprinting is missing! 
Needs to be updated!!!

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/Nikolaev2010-F2}
  \caption{
    \textbf{a:}\textbf{b:}\textbf{c:}\textbf{d:}\textbf{e:}\textbf{f:}
  }
  \label{fig:nikolaev2010}
\end{figure}

Cardio-myocytes exhibit a unique topography with transverse (T-)tubules and
crests (Fig.~\ref{fig:nikolaev2010}a, b). By first recording the topography
and subsequently moving the SICM pipette to either a T-tubule or a crest,
followed by the local application of agonists of either the $\beta_1$- or
$\beta_2$-adrenergic receptor (AR) and recording the intensity ratio of cyan
and yellow fluorescent protein, coupled to a Förster resonance energy transfer
(FRET) based reporter of cyclic AMP (Fig.~\ref{fig:nikolaev2010}c--f), it was
shown that the distribution of the $\beta_2$-AR was altered in failing
cardio-myocytes \cite{Nikolaev2010}. Furthermore, this approach was used to
investigate the effect of partial mechanical unloading, showing that it
reduces the cyclic AMP response of $\beta_2$-ARs at the T-tubules
\cite{Wright2018}. To investigate the distribution of the $\beta_3$-AR, the
approach was extended to use a FRET-based reporter of cyclic GMP, showing that
a redistribution of the $\beta_3$-AR occurs in failing cardio-myocytes, too
\cite{Schobesberger2020}.

>>>>

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/Nikolaev2010-F2}
  \caption{
    \textbf{Distribution of $\beta_1$- and $\beta_2$-adrenergic receptors (AR) on the surface of cardiomyocytes obtained from healthy rats.}
    \textbf{a:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, where the stimulation of the $\beta_1$-AR was take place.
    \textbf{b:} F\"orster resonance energy transfer (FRET) YFP/CFP (yellow and cyan fluorescent protein) ratio after $\beta_1$-AR stimulation in the crest of the cell (a). 
    \textbf{c:} FRET YFP/CFP ratio after $\beta_1$-AR stimulation in the T-tubule of the cell (a).
    \textbf{d:} SICM image of a cardiomyocyte surface. The white arrows indicate the positions, where the stimulation of the $\beta_2$-AR was take place. 
    \textbf{e:} FRET YFP/CFP ratio after $\beta_2$-AR stimulation in the crest of the cell (c).
    \textbf{f:} FRET YFP/CFP ratio after $\beta_2$-AR stimulation in the T-tubule of the cell (c).
    ICI: ICI118551 is a $\beta_2$-AR antagonist; CGP: CGP20712A is a $\beta_1$-AR antagonist
    A decrease in the FRET YFP/CFP ratio between YFP and CFP indicates an increase in cAMP.
  }
  \label{fig:nikolaev2010}
\end{figure}

Cardio-myocytes exhibit a unique topography with transverse (T-)tubules and
crests (Fig.~\ref{fig:nikolaev2010}a, d). By first recording the topography
and subsequently moving the SICM pipette to either a T-tubule or a crest,
followed by the local application of agonists of either the $\beta_1$- or
$\beta_2$-adrenergic receptor (AR) and recording the intensity ratio of cyan
and yellow fluorescent protein, coupled to a Förster resonance energy transfer
(FRET) based reporter of cyclic AMP (Fig.~\ref{fig:nikolaev2010}b, c, e, f), it was
shown that the distribution of the $\beta_2$-AR was altered in failing
cardio-myocytes \cite{Nikolaev2010}. Furthermore, this approach was used to
investigate the effect of partial mechanical unloading, showing that it
reduces the cyclic AMP response of $\beta_2$-ARs at the T-tubules
\cite{Wright2018}. To investigate the distribution of the $\beta_3$-AR, the
approach was extended to use a FRET-based reporter of cyclic GMP, showing that
a redistribution of the $\beta_3$-AR occurs in failing cardio-myocytes, too
\cite{Schobesberger2020}.
